Should I Airbnb My Property?

### 2017-03-20 abb_Writeup.Rmd
Add R package citations

Unfortunately both data sources for this work are proprietarily licenses and are not able to be shared by the authors.  All the code used to complete this analysis, done in the R language, is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.  An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at **[andykrause/shinyapps.io/shouldiairbnb](https://andykrause.shinyapps.io/ShouldIAirbnb)**.

>>>>

Unfortunately both data sources for this work are proprietarily licenses and are not able to be shared by the authors.  All the code used to complete this analysis, done in the R language^[Using the following packages: \texttt{sp} [@sp], \texttt{maptools} [@maptools], \texttt{ggplot2} [@ggplot2], \texttt{xtable} [@xtable], \texttt{ggmap} [@ggmap], \texttt{plyr} [@plyr], \texttt{reshape2} [@reshape2], \texttt{stringr} [@stringr], \texttt{knitr} [@knitr], \texttt{rmarkdown} [@rmarkdown], \texttt{lmtest} [@lmtest], \texttt{ROCR} [@ROCR], and \texttt{kernlab} [@kernlab]], is available for download at **[www.github.com/andykrause/airbnbmelbourne](https://www.github.com/andykrause/airbnbmelbourne)**.  An interactive website that allows readers to examine additional facets, breakdown and subsets of the data and the resulting analytical results can be found at **[andykrause/shinyapps.io/shouldiairbnb](https://andykrause.shinyapps.io/ShouldIAirbnb)**.
